Index measures for oak decline severity using phenotypic descriptors

### 2019-12-10 manuscript/manuscript.Rmd
manuscript now rendered as a word document. Added to introduction. Added references

---
title: "Index measures for oak decline severity using phenotypic descriptors"
output: 
  bookdown::pdf_document2:
   toc: false
   number_sections: false
   keep_tex: no
---

@@

Random forest is an ensemble machine learning

Unsupervised learning ...

Here, we propose a framework for quantitatively measuring the phenotypic severity of oak decline that is based on unsupervised random forest machine learning

>>>>

---
title: "Index measures for oak decline severity using phenotypic descriptors"
output: 
  bookdown::word_document2:
   toc: false
bibliography: references.bib
---

@@

Machine learning is finding increasing utility in biological and geographical applications due to it's...
A popular algroith is that of random forest due to it's versatility, relatively trivial training requirements and resiliance against overfitting [@breiman2001] (refs). 
It is an ensemble machine learning method where forests of bootstrap sampled decision trees are grown, yielding both out of bag (OOB) sample prediction accuracies and variable importance.
Unsupervised learning is also possible

Here, we propose a framework to enable quantitative visible oak decline severity measurement that utilises a range of targeted phenotypic descriptors and unsupervised random forest machine learning.
These measures include:
